Classless Java

### 2015-11-17 paper/sections/Appendix.tex
Typo.

\subsection{Proof of LEMMA 1}\label{subsec:proof1}
\begin{proof}
First for convenience, assume that $\II_0$ is of form $$\mixinAnn\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC \methods\ \cC$$
It suffices to prove $\dom'(\C_0)=\dom(\C_0)\cup\dom(\methods')$.
\begin{itemize}
\item If $m\notin\dom(\methods')$, by the definition of $\mBody$, it is obtained from $\override$. The first argument of $\override$, namely $\methods\cup\methods'(m)$, is equal to $\methods(m)$, and the second argument is not changed as well, thus the result of $\override$ is not changed during translation. Hence $m\in\dom'(\C_0)$ iff $m\in\dom(\C_0)$.
\item If $m\in\dom(\methods')$, we are to prove $m\in\dom'(\C_0)$. So if $m$ is the $\QM{of}$ method generated by $\ofMethod$, its $\mBody$ value is well defined, by the rule $\override(\method,\none)=\method$. On the other hand, if $m$ is generated by $\otherMethod$, namely $m$ is a $\QM{with-}$ or setter method, we can also get its $\mBody$ value, since in the definition of $\otherMethod$, we can see $\isWith$ and $\isSetter$ ensure the compatible subtyping relationship. Hence $m\in\dom'(\C_0)$ as well.
\end{itemize}
\end{proof}

\subsection{Proof of LEMMA 2}\label{subsec:proof2}
\begin{proof}
By the rule \rn{t-Invk} in Figure~\ref{ET}, we divide it into two parts.

>>>>

\subsection{Proof of LEMMA 1}\label{subsec:proof1}
\begin{proof}
It suffices to prove $\dom([\![\II_0]\!])=\dom(\C_0)\cup\dom(\methods')$.
\begin{itemize}
\item If $m\notin\dom(\methods')$, by the definition of $\mBody$, it is obtained from $\override$. The first argument of $\override$, namely $\methods\cup\methods'(m)$, is equal to $\methods(m)$, and the second argument is not changed as well, thus the result of $\override$ is not changed during translation. Hence $m\in\dom([\![\II_0]\!])$ iff $m\in\dom(\C_0)$.
\item If $m\in\dom(\methods')$, we are to prove $m\in\dom([\![\II_0]\!])$. So if $m$ is the $\QM{of}$ method generated by $\ofMethod$, its $\mBody$ value is well defined, by the rule $\override(\method,\none)=\method$. On the other hand, if $m$ is generated by $\otherMethod$, namely $m$ is a $\QM{with-}$ or setter method, we can also get its $\mBody$ value, since in the definition of $\otherMethod$, we can see $\isWith$ and $\isSetter$ ensure the compatible subtyping relationship. Hence $m\in\dom([\![\II_0]\!])$ as well.
\end{itemize}
\end{proof}

\subsection{Proof of LEMMA 2}\label{subsec:proof2}
\begin{proof}
By the rule \rn{t-Intf} in Figure~\ref{ET}, we divide it into two parts.
